S-Tipping vs B-Tipping

### 2018-05-16 paper/paper.Rmd
i cant use epa affiliation unless my advisors are on the project .... easier to just do this :)

---
title: S-Tipping vs B-Tipping
## We can figure out author order later on who end up doing more etc :-)
author:
  - name: Ryan Batt
    affiliation: epa
  - name: Carl Boettiger
    email: cboettig@berkeley.edu
    affiliation: espm
    footnote: Corresponding Author

>>>>

---
title: S-Tipping vs B-Tipping
## We can figure out author order later on who end up doing more etc :-)
author:
  - name: Ryan Batt
    affiliation: Rensselaer Polytechnic Institute and Rutgers University
  - name: Carl Boettiger
    email: cboettig@berkeley.edu
    affiliation: espm
    footnote: Corresponding Author
